Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Explain how Boolean nodes were implemented

>>>>

The Boolean operations required by the two approaches were implemented as two
separate nodes.  Currently both nodes take two cubes, which are assumed to be
axis-aligned.  {\tt BooleanAndNode} finds the intersection of the two cubes by
finding the minimums and maximums of the cubes in world space.  {\tt
BooleanXorNode} does the same, but then uses a variation of the well-known
Sutherland-Hodgman polyline-clipping algorithm to break up the cubes into pieces
around the intersection.  Both nodes use the {\tt NodeListener} interface to
only update their geometry when the cubes move.
